Emissions and Perceptions of Climate Change

### 2022-11-30 Code/Drafts/LongVersion_Oral_Presentation.Rmd
Oral Presentation Preparation

>CAIT Data by (World Resource Institute) WRI from 1990-2019 including all emissions and per capita

>Survey Data 2022 from Yale on Facebook, was in wide format but had more questions

@@

```{r, echo=FALSE}
emissions$year<-paste0("01-01-", emissions$year)
```

@@

Lets determine if there is a difference in rate from when both country's emissions started significantly decreasing and the rate is consistently negative 2010.
```{r, echo=FALSE}
emissions_rate_2010<- emissions_rate %>% 
  filter(emissions_rate$year>="2010-01-01")

@@

@@

This survey question asked people if their region should use more or less fossil fuels with the options being much more, somewhat more, same as today (same amount), somewhat less, or much less.

```{r,echo=FALSE}
#Parcing out just the survey answers regarding climate change beliefs
fuels<- survey %>% filter(survey$question=="Ques__Fossil_moreorless") 
```

```{r, warning=FALSE, echo=FALSE}
# Making the graph
ggplot(fuels, aes(response,Number, fill=Country))+geom_bar(stat = 'identity',
  position = 'dodge') + 
  labs(title="Fossil Fuel Use", x="Response to Survey Question", y="Percent") + 
  # renaming x and y axis labels
  theme_bw() +
  coord_flip() # switching x and y axis to read the suvey questions
```

Figure 3. The fossil fuel usage Danes and Americans think their area should use. Response is in percentage of the total surveyed.

@@

```{r,warning=FALSE}
ggplot(fuels, aes(x="", y= Number, fill=response))+  
  geom_bar(stat="identity", width=1)+ coord_polar("y", start=0) + 
   geom_label(aes(label = round(Number, digits = 1)), nudge_x = 0.4) +
  # add percentages
  theme_void()+ # remove background, grid, numeric labels
facet_wrap(~Country)
```

@@

want to try ***Diverging stacked bar chart instead***

>>>>

>CAIT Data by (World Resource Institute) WRI from 1990-2019 including all emissions and per capita
> Survey Data 2022 from Yale on Facebook, was in wide format but had more questions

@@

```{r}
emissions$year<-paste0("01-01-", emissions$year)
```

@@

Lets determine if there is a difference in rate from when both country's emissions started significantly decreasing and the rate is consistenly negative 2010.
```{r}
emissions_rate_2010<- emissions_rate %>% 
  filter(emissions_rate$year>="2010-01-01")

@@

Though more people may have been interviewed in one country than the other, the survey data is in percent, as in the percentage out of the whole who chose that option. We can double check to ensure the recorded numbers equals 100 per country per survey question.

Lets check with the 'beliefs question' which is the first question we will analyzed.

```{r}
#Parsing out just the survey answers regarding climate change beliefs
beliefs<- survey %>% filter(survey$question=="Ques__Climate_beliefs") 
```

#### Beliefs of Climate Change

Lets first see what Danes and Americans believe caused climate. The options to choose from were: caused mostly by humans, caused by natural change in the environment, caused by both, and climate change is not happening.

```{r, warning=FALSE, echo=FALSE}
# Making the graph
ggplot(beliefs, aes(response,Number, fill=Country))+
  geom_bar(stat = 'identity', position = 'dodge') + 
 labs(title="Cause of Climate Change", x="Response to Survey Question",
      y="Percent") + # titling and renaming x and y axis labels
  coord_flip()+
  theme_bw()

Figure 1. What Danes and Americans believe caused climate change. Responses are in percent of the total surveyed.

More Americans believe that climate change is not happening or that it is caused by natural changes than Danes. More Danes believe it is caused by human activities. However, more Danes than Americans think it is cause equally by both. Lets look at a pie chart as well.

```{r, warning=FALSE, results='hold'}
piecolor<- c("orange","maroon","darkgreen","lightblue", "gray70","purple")

beliefs<- beliefs %>% arrange(desc(Number)) %>% 
  mutate(Position=cumsum(Number/2)-0.5*Number) # moving the percentage labels around
legend<- c("caused equally","caused mostly by humans",
           "caused mostly by natural changes","climate change isin't happening",
           "other","refused") #see below
ggplot(beliefs, aes(x="", Percent, y= Number, fill=response))+  
  geom_bar(stat="identity", width=1, color="white")+
  coord_polar("y", start=0) + 
  facet_wrap(~Country)+
 #legend( 3, legend=legend)+, attempt to make the legends smaller, 
  #so the pie charts could be bigger and I could move the percentages.
  scale_fill_manual(values=piecolor )+ # manually fill the color
   theme_void()+# remove background, grid, numeric labels
  geom_label(aes (label = round(Number, digits = 1), x=1.7),color="white", size=4) 
# add percentages

Figure 2. Pie chart of what Danes and Americans believe caused climate change. Responses are in percent of the total surveyed.

The pie chart shows that most of the Danes surveyed believe climate change is human caused, whereas more Americans thought it was a mix of human and natural causes or that climate change is not happening.

Lets run a statistical test to see if Danes believe climate change is human caused significantly more than Americans.

We have multiple categorical predictor variables with the response variable being ratio data that bounded between 0 and 100%, so we will run a ***chi-squared test*** after converting percents to numbers by multiplying the percents times the total number of repsondants to that question per country.

1101 people answered in Denmark
3096 answered in United States

### Running the Statistical Test
```{r}
dumb_way<- c(1101,3096,1101,3096,1101,3096,1101,3096,1101,3096,1101,3096) 
#1101 Danes answered the survey, 3096 Americans did.
beliefs$num_people<- dumb_way #put that vector into here

beliefs<- beliefs %>% group_by(Country, response) %>% 
  mutate(total=(Number/100)*num_people) #calculating rate where Number=percentage

beliefs$total<- round(beliefs$total, digits=0) #round to whole number

beliefs_numPeople<- beliefs %>% select(response, Country, total)
```

Creating a matrix by hand
```{r}
vector_Den<- c(585,57,419,19,16,1)
vector_US<-c(1295,473,1073,86,161,7)
matrix<- as.matrix(rbind(vector_Den, vector_US))
chisq.test(matrix)
```
There is a significant difference in how Danes and Americans answered this survey question.

### Level of worriedness about Climate Changed

In this survey question people were asked how worried they are about climate change. There are three options for 
```{r, echo=FALSE}
worry<- survey %>% filter(survey$question=="Ques__climate_worry") 
```

```{r, echo=FALSE}
ggplot(worry, aes(response,Number, fill=Country))+
  geom_bar(stat = 'identity', position = 'dodge') + 
  labs(title="Level of Concern Over Climate Change", 
       x="Response to Survey Question", y="Percent") + theme_bw() + coord_flip()
```

Figure 3. Bar graph of the Level of Concern over climate change of both Danes and Americans. Response is in percentage of the total surveyed.

32% of Americans are very worried about climate change, wherease oonly 21% of Danes are. But 52% of Danes are somewhat worried at only 36% are. To better visualize this lets try another graph.

```{r, echo=FALSE}
ggplot(worry, aes(x="", y= Number, fill=response))+  geom_bar(stat="identity",
    width=1)+ coord_polar("y", start=0) + 
   geom_label(aes(label = round(Number, digits = 1)), nudge_x = 0.4) + 
  # add percentages
  theme_void()+ # remove background, grid, numeric labels
facet_wrap(~Country)
```

Figure 4. Pie chart of the Level of Concern over climate change of both Danes and Americans. Response is in percentage of the total surveyed.

We can see that most Danes are somewhat worried, with the smallest percentage being not worried at all. Most Americans are also somewhat worried, though the percentage is smaller compared too Denmark (51% to 35.6%). More Americans however are very worried, and more Americans are not at all worried than Danes. Interesting. A statistical test is needed to see if Americans are less worried than Danes.

#### Lets do a statistical test to verify.

```{r, echo=FALSE}
dumb_way<- c(1101,3096,1101,3096,1101,3096,1101,3096,1101,3096) 
#1101 Danes answered the survey, 3096 Americans did.
worry$num_people<- dumb_way #put that vector into here

worry<- worry %>% group_by(Country, response) %>%  
  mutate(total=(Number/100)*num_people) #calculating rate where Number=percentage

worry$total<- round(worry$total, digits=0) #round to whole number

worry_numPeople<- worry %>% select(response, Country, total)
```

Creating a matrix by hand
```{r, echo=FALSE}
w_Den<- c(228,561,261,49,1)
w_US<-c(991,1102,502,498,3)
w_matrix<- as.matrix(rbind(w_Den, w_US))
chisq.test(w_matrix)
```
There is a significant difference in how Danes and Americans answered this survey question.

### Is Climate Change a Big Threat

In this survey question people were asked whether or not climate change is a big threat within the next 20 years. The options were very serious threat, somewhat serious, not a threat at all, or I do not know.

```{r, echo=FALSE}
threat<- survey %>% filter(survey$question=="Ques__threat_20_years") 
```

```{r, echo=FALSE}
ggplot(threat, aes(response,Number, fill=Country))+
  geom_bar(stat = 'identity', position = 'dodge') + 
  labs(title="Perceieved Threat of Climate Change", 
       x="Response to Survey Question", y="Percent") + theme_bw() + coord_flip()
```

Figure 5. Bar graph of the perceieved threat of climate change of Danes and Americans. Response is in percentage of the total surveyed.

More Americans than Danes think that climate change is a very serious threat, but Danes think it is a somewhat serious threat than Americans. More Americans also think that climate change is not a threat at all than Danes. Lets view a pie chart.

```{r, echo=FALSE}
ggplot(threat, aes(x="", y= Number, fill=response))+  
  geom_bar(stat="identity", width=1)+ coord_polar("y", start=0) + 
   geom_label(aes(label = round(Number, digits = 1)), nudge_x = 0.5, nudge_y=2) + 
  # add percentages
  theme_void()+ # remove background, grid, numeric labels
facet_wrap(~Country)
```

Figure 6. Pie char of the perceieved threat of climate change of Danes and Americans. Response is in percentage of the total surveyed.

We can see that most Danes, %53 think climate change is a somewhat serious threat, wherease most Americans, %40.6, think it is a very serioous threat. Only 17.5% of Danes think that it is not a threat at all, compared to the 22.3% of Americans that think that. Lets test with a statistical test.

#### Lets do a statistical test to verify.

```{r, echo=FALSE}
dumb_way<- c(1101,3096,1101,3096,1101,3096,1101,3096,1101,3096) 
#1101 Danes answered the survey, 3096 Americans did.
threat$num_people<- dumb_way #put that vector into here

threat<- worry %>% group_by(Country, response) %>%  mutate(total=(Number/100)*num_people)
#calculating rate where Number=percentage

threat$total<- round(threat$total, digits=0) #round to whole number

threat_numPeople<- threat %>% select(response, Country, total)
```

Creating a matrix by hand
```{r, echo=FALSE}
t_Den<- c(228,561,261,48,1)
t_US<-c(991,1102,502,498,3)
t_matrix<- as.matrix(rbind(t_Den, t_US))
chisq.test(t_matrix)
```
Again, there is a significant difference in how Danes and Americans answered this survey question.

@@

Now that we know what Danes and Americans think about climate change and how worried they are, lets see how they are reacting. This next survey question asked people if their region should use more or less fossil fuels with the options being much more, somewhat more, same as today (same amount), somewhat less, or much less.

Lets check with the 'beilefs question' which is the first we will anaylzed.

```{r, echo=FALSE}
#Parcing out just the survey answers regarding climate change beliefs
fuels<- survey %>% filter(survey$question=="Ques__Fossil_moreorless") 
```

```{r, echo=FALSE, warning=FALSE}
# Making the graph
ggplot(fuels, aes(response,Number, fill=Country))+geom_bar(stat = 'identity',
  position = 'dodge') + 
  labs(title="Fossil Fuel Use", x="Response to Survey Question", y="Percent") + 
  # renaming x and y axis labels
  theme_bw() +
  coord_flip() # switching x and y axis to read the suvey questions
```

Figure 7. The fossil fuel usage Danes and Americans think their area should use. Response is in percentage of the total surveyed.

@@

```{r, echo=FALSE, warning=FALSE}
ggplot(fuels, aes(x="", y= Number, fill=response))+  
  geom_bar(stat="identity", width=1)+ coord_polar("y", start=0) + 
   geom_label(aes(label = round(Number, digits = 1)), nudge_x = 0.4) +
  # add percentages
  theme_void()+ # remove background, grid, numeric labels
facet_wrap(~Country)
```

@@

want to try Diverging stacked bar chart instead
